---
output:
  github_document:
    html_preview: false
---

```{r readme-01, echo = FALSE}
knitr::opts_chunk$set(
  fig.asp = 2/3,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# photobiologyFilters

[![CRAN version](https://www.r-pkg.org/badges/version-last-release/photobiologyFilters)](https://cran.r-project.org/package=photobiologyFilters) 
[![cran checks](https://cranchecks.info/badges/worst/photobiologyFilters)](https://cran.r-project.org/web/checks/check_results_photobiologyFilters.html)

Package **photobiologyFilters** is a collection of spectral transmittance data for more than 300 filters measured in our lab, by collaborators or for which data have been made available by the suppliers for inclussion in this package.

## Code breaking renaming of data objects

In the update to version 0.5.0 several members of the collection of filter spectra were
renamed to ensure consistency and clarity. As of version 0.5.0 all member names
start with the name of the manufacturer or supplier. In addition, several of the vectors
of names of member spectra were renamed to include the word "filters" to avoid possible
name clashes with other packages and also to improve naming consistency.

## Examples

```{r example-02, message=FALSE}
library(photobiologyFilters)
```

How many spectra are included in the current version of 'photobiologyFilters'?

```{r example-03}
length(filters.mspct)
```

What are the names of available spectra. We use `head()` to limit the output.

```{r example-04}
# list names of the first 10 filters
head(names(filters.mspct), 10)
```

To subset based on different criteria we can use predefined character vectors of filter names. For example, vector `polyester` lists the names of the spectra for filters made of polyester (PET). 

```{r example-05}
polyester_filters
```

We can use the vector to extract all these spectra as a collection.

```{r example-05a}
filters.mspct[polyester_filters]
```

The package includes a character vector with the names of these vectors of names that are available.

```{r example-05b}
all_filter_accessors
```

Please, see the _User Guide_ or documentation
for the names of other vectors of names for materials, suppliers, and regions of
the spectrum.

Summary calculations can be easily done with methods from package 'photobiology'. Here we calculate mean transmittance for two regions of the spectrum given by wavelengths in nanometres.

```{r example-06}
transmittance(filters.mspct[["Foiltek_Clear_PET_G"]], 
              list(waveband(c(250, 315)), waveband(c(500,600))))
```

The `autoplot()` methods from package 'ggspectra' can be used for plotting one or more spectra at a time. The classes of the objects used to store the spectral data are derived from `"data.frame"` making direct use of the data easy with functions and methods 
from base R and various packages.

## Installation

Installation of the most recent stable version from CRAN:

```{r, eval=FALSE}
install.packages("photobiologyFilters")
```

Installation of the current unstable version from Bitbucket:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_bitbucket("aphalo/photobiologyfilters")
```

## Documentation 

HTML documentation is available at (https://docs.r4photobiology.info/photobiologyFilters/), including a _User Guide_.

News on updates to the different packages of the 'r4photobiology' suite are regularly posted at (https://www.r4photobiology.info/).

Two articles introduce the basic ideas behind the design of the suite and its use:
Aphalo P. J. (2015) (https://doi.org/10.19232/uv4pb.2015.1.14) and Aphalo P. J. (2016)  (https://doi.org/10.19232/uv4pb.2016.1.15).

A book is under preparation, and the draft is currently available at (https://leanpub.com/r4photobiology/).

A handbook written before the suite was developed contains useful information on the quantification and manipulation of ultraviolet and visible radiation:
Aphalo, P. J., Albert, A., Björn, L. O., McLeod, A. R., Robson, T. M., & Rosenqvist, E. (Eds.) (2012) Beyond the Visible: A handbook of best practice in plant UV photobiology (1st ed., p. xxx + 174). Helsinki: University of Helsinki, Department of Biosciences, Division of Plant Biology. ISBN 978-952-10-8363-1 (PDF), 978-952-10-8362-4 (paperback). PDF file available from (https://hdl.handle.net/10138/37558).

## Contributing

Pull requests, bug reports, and feature requests are welcome at (https://bitbucket.org/aphalo/photobiologyfilters).

## Citation

If you use this package to produce scientific or commercial publications, please cite according to:

```{r}
citation("photobiologyFilters")
```

## License

© 2012-2020 Pedro J. Aphalo (pedro.aphalo@helsinki.fi). Released under the GPL, version 2 or greater. This software carries no warranty of any kind.

