---
title: "`photobiologyFilters` `r packageVersion('photobiologyFilters')`<br>Data Catalogue"
author: "Pedro J. Aphalo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data Catalogue}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
knitr::opts_chunk$set(fig.width=8, fig.height=4)
```


## Introduction

This is a catalogue of all data sets included in the package. You will find below plots of the emission spectra of different lamps. All spectra are normalized to an area of one at the peak of the curve.

The spectral data have been acquired with different instruments. These spectrometers
differ in their wavelength resolution giving for the same filters measured slopes of different steepness when peaks or valleys are narrow. This is an inevitable artefact of spectral measurements.

As this package includes data for over a hundred different filters, they are plotted
in groups rather than individually.

```{r}
library(photobiology)
library(photobiologyWavebands)
library(photobiologyFilters)
library(ggplot2)
library(ggspectra)
```


```{r}
options(photobiology.plot.annotations =
          c("boxes", "labels", "colour.guide", "peaks", "title"))
```

## Accessing data for a filter

```{r}
cat(comment(filters.mspct$UG11))
plot(filters.mspct$UG11)
```

## List of all filters

```{r}
names(filters.mspct)
```

## Ionic glass filters

### Schott

```{r}
schott
```

### Heliopan (Schneider)

### Other suppliers

## Interference filters

## Regular glass

## Plastic sheets

```{r}
plexiglas
foiltek
```

## Plastic films

### Technical films

```{r}
mcdermit
acetate
etola
```

### Theatrical gels

```{r}
lee
rosco
```


### Greenhouse cladding materials

```{r}
bpi_visqueen
xl_horticulture
# others
```


## Objects

### Labware

```{r}
petri_dishes
```


